%-----------Experience-----------%
\section{Experience}
\resumeSubHeadingListStart
    
\resumeProjectHeading
{\textbf{Aryvo (formerly CabMyRide)} $|$ \emph{Software Engineer}} {{04/2025 -- Present} $|$ {United Kingdom (Remote)}}
\hrulefill
\resumeItemListStart
    \resumeItem{Architected scalable Flutter apps using \textbf{Clean Architecture + Riverpod}, delivering a modular, testable cross-platform codebase.}
    \resumeItem{ Implemented functional programming techniques using Dartz and Freezed to create type-safe error handling and immutable models, resulting in a 40\% reduction in bug reports during the testing phase of new features.}
    \resumeItem{Implemented \textbf{real-time location tracking and background services} to ensure reliable live trip updates across app states.}
    \resumeItem{Built secure \textbf{multi-channel payments} with Stripe (Apple Pay, wallets) and SumUp, supporting subscriptions and tipping.}
    \resumeItem{Developed \textbf{real-time chat and observability} using Twilio, FCM, Sentry, Mixpanel, and OpenTelemetry.}
    \resumeItem{Implemented \textbf{iOS Live Activities} (Swift + Flutter bridge) for real-time ride updates on Lock Screen and Dynamic Island.}
    \resumeItem{Enabled production-ready delivery with \textbf{Shorebird OTA updates}, deep linking, multi-flavor builds, and secure storage.}
%   \resumeItem{Links: {%
% \textbf{Customer App:} \href{https://apps.apple.com/us/app/myride-partner/id6670173134}{iOS} $|$ \href{https://play.google.com/store/search?q=cabmyride&c=apps&hl=en}{Android} \newline
% \textbf{Driver App:} \href{https://apps.apple.com/us/app/myride-partner/id6670173134}{iOS} $|$ \href{https://play.google.com/store/search?q=myride%20parnter&c=apps&hl=en}{Android}%
% }}


\resumeItemListEnd

\resumeProjectHeading
{\textbf{DSMO PVT LTD.} $|$ \emph{Software Engineer Intern}} {{08/2024 -- 10/2024} $|$ {Kolkata (Remote)}}
\hrulefill
\resumeItemListStart
    \resumeItem{Restructured the Flutter codebase using \textbf{Clean Architecture}, reducing module coupling and improving long-term maintainability.}
    
    \resumeItem{Implemented \textbf{Provider-based state management} to optimize widget rebuilds and improve UI responsiveness.}
    
    \resumeItem{Refactored core navigation and screen flows to enforce clearer separation of concerns and faster feature iteration.}
\resumeItemListEnd


\resumeSubHeadingListEnd
