%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Plaudern} $|$ \emph{Flutter, Firebase}}    {}
    \hrulefill
    \resumeItemListStart
        \resumeItem {Spearheaded the design and implementation of a cutting-edge mobile messaging app using Flutter framework; seamlessly optimized user experience via Firebase, resulting in a 30\% increase in user engagement}
        \resumeItem{our data-driven approach, utilizing Firebase Analytics, sets us apart with a remarkable 25\% boost in user retention and engagement, providing unparalleled insights for targeted improvements and superior customer satisfaction.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Real Block} $|$ \emph{Flutter, Solidity, Node.js, Web3.js}}    {}
    \hrulefill
    \resumeItemListStart
        \resumeItem {Implemented an immutable ledger using Solidity Smart Contracts, ensuring transparent and secure transaction records for a diverse range of real estate assets.}
        \resumeItem{ Real Block innovates real estate tech with Solidity, Flutter, Node.js, and Web3.js. Uniquely combining secure ledgers and an intuitive Flutter frontend, we redefine user experiences and transaction transparency.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{MoneyTrees} $|$ \emph{ReactJS, Node.js, Solidity, Web3.js}}{}
    \hrulefill
    \resumeItemListStart
        \resumeItem{ Engineered a reward system using Solidity and web3.js, boosting user engagement by 25\% and establishing a seamless plant-buying experience.}
        \resumeItem{Revolutionizing plant commerce, Money Trees integrates blockchain rewards. Purchases earn personalized tokens, stakable for more greenery. React.js, Solidity, \& Web3.js makes it a pioneering and rewarding botanical experience.}
    \resumeItemListEnd

     \resumeProjectHeading
    {\textbf{MIXTUR3} $|$ \emph{ReactJS, Node.js, Web3.js, Truffle, Solidity}}{}
    \hrulefill
    \resumeItemListStart
        \resumeItem{MIXTUR3 revolutionizes music commerce, empowering artists to sell songs as exclusive NFTs. It forges a distinct path in reshaping the real-world music industry.}
        \resumeItem{Engineered and deployed ERC721 Solidity smart contracts to revolutionize transaction transparency; ensured artists received equitable compensation for their work and secured transactions, reducing fraud risk by 40\%. }
    \resumeItemListEnd

    % \resumeProjectHeading
    % {\textbf{Bitcoin Ticker} $|$ \emph{Flutter, REST API}}{}
    % \hrulefill
    % \resumeItemListStart
    %     \resumeItem{Created a user-friendly application that provides real-time cryptocurrency prices, enhancing market awareness and facilitating quick access to accurate Bitcoin prices through seamless Flutter interface and RESTful API integration.}
    % \resumeItemListEnd
\resumeSubHeadingListEnd
